---
title: "Attempt to Confuse Inheritance"
output: html_document
---

Let's see if we can confuse R by defining a class with multiple parent classes,
such that parents have methods with the same name (but doing slightly different
things).
```{r, results='hide'}
setClass("parent1", slots=c(x="numeric"))
setClass("parent2", slots=c(y="numeric"))
setClass("parent3", slots=c(z="logical"))
setClass("poorChild", contains=c("parent2", "parent1", "parent3"))
setGeneric("icanconfuse", function(obj, ...) standardGeneric("icanconfuse"))
setMethod("icanconfuse", signature = (obj="parent1"),
          definition=function(obj) print("I am from parent 1"))
setMethod("icanconfuse", signature = (obj="parent2"),
          definition=function(obj) print("I am from parent 2"))
setMethod("icanconfuse", signature = (obj="parent3"),
          definition=function(obj) print("I am from parent 3"))
```
Let's create instances of all three superclasses and one subclass.
```{r}
instP1 <- new("parent1", x=11)
instP2 <- new("parent2", y=11)
instP3 <- new("parent3", z=TRUE)
instCh <- new("poorChild", x=33, y=44, z=FALSE)
```
Applying `icanconfuse` method to parents
```{r}
icanconfuse(instP1)
icanconfuse(instP2)
icanconfuse(instP3)
icanconfuse(instCh)
```
Well ... it didn't get confused.  Despite the fact that there are three 
`icanconfuse` methods upstream the inheritance graph the ambiguity was resolved
by simply picking the first one in line.  The order of parents defined by the
way they provided in the `contains` argument of the `setClass` function.
