---
title: "S4 setIs(.) part I"
output: html_document
---

`setIs` function is a way to establish relationship between the S4 classes.

```{r}
# To be superclass.
setClass("A", slots=c(x="numeric"))
# To be subclass.  It has more details - i.e. more slots
setClass("B", slots=c(x="numeric", y="character"))
```
Let's take a look at classes
```{r}
getClass("A")
getClass("B")
```
There is no simple or explicit relatioship between the classes. 
Thus coercion won't work.
```{r, error=TRUE}
instA <- new("A", x=1)
instB <- new("B", x=2, y="b")
as(instA, "B")
as(instB, "A")
```
Explicitely setting the inheritance relationship with `setIs`.
Note, class `B` constains all the slots from class `A`.
Thus coercing is trivial. Basically it is subsetting of `B` the slots
```{r}
# since slots of B is a subset of A 
setIs("B", "A")  
```
Let's take a look at classes again. Now `B` is listed as subclass of `A`.
```{r}
getClass("A")
getClass("B")
```
Now, coercion works both ways.
```{r}
as(instA, "B")
as(instB, "A")
```



