---
title: "S4 setIs(.) Part II"
output: html_document
---

`setIs` function is a way to establish relationship between the S4 classes.
If the superclass has less slots and coversely subclass contains additional 
information (that is slots), then establishing inheritance with `setIs` is
seamless.  How about the situation when superclass-to-be contains more slots
then subclass-to-be?
```{r}
# To be superclass.
setClass("A", slots=c(x="numeric", y="character"))
# To be subclass.  Note the slot @y is not present.
setClass("B", slots=c(x="numeric"))
```
Attempt to set `B` as subclass of `A` results in an error.
```{r, error=TRUE}
setIs("B", "A")  
```
Obviously coercion from one class to another won't work either.
```{r, error=TRUE}
instA <- new("A", x=1, y="b")
instB <- new("B", x=2)
as(instA, "B")
as(instB, "A")
```
It needs a coerce and a replace functions. The coerce function 
is kind of obvious, it just needs to tell what to do with this new slot @y.
The replace, however, is a bit less obvious.  It does not casts the object to the 
superclass, but replaces the parts corresponding to the superclass by the 
assigned `<-` value.
```{r}
setIs("B", "A",
      coerce = function(obj) {
          out <- new("A")
          out@x <- obj@x
          out@y='dummy' 
          return(out)},
      replace = function(obj, value) {
          obj@x <- value@x
          return(obj)})

```
The relationship between the classes has been established. 
`B` extends (or `is`) `A`, but not the other way around.
```{r, error=TRUE}
extends("B","A")
is(instB,"A")
extends("A","B")
is(instA,"B")
```
Let's see how the coerce works now.
```{r}
as(instA, "B")
as(instB, "A")
```
The replace
```{r}
show(instB)
anotherA <- new("A", x=55, y="abc")
as(instB, "A") <- anotherA
show(instB)
```
The replacement of `A` with `B` does not work, although that should be
a simple replacement of @x slot (I think)
```{r, error=TRUE}
as(instA, "B") <- new("B", x=33)
```
