---
title: "sigmoids"
output: html_document
---

[Link to the Rmd file on GitHub](https://github.com/vladpetyuk/snippets/blob/master/sigmoids.Rmd)

### Sigmoid Function

### $\frac{p_1}{(1+e^{-p_2 \times (x - p_3)})}$

`p1` is the full scale from 0 to p1. For logistic regression it is 1.
In the later examples it will be hardcoded as 1.

`p2` is the sharpness of change.

`p3` x position of the 50% height.

```{r chunk1}
sigmoid = function(x, p1, p2, p3) {p1 / (1 + exp(-p2 * (x - p3)))}
curve(sigmoid(x, p1=1, p2=2, p3=-3), from=-10, to=+10)
abline(v=-3, lty=2)
```




***

### Sigmoid that starts at zero.

Sometimes we want to convert a parameter that varies only as $(0,+\infty)$
instead of $(-\infty,+\infty)$. First, to convert `x` form $(0,+\infty)$ to 
$(-\infty,+\infty)$ we'll take the `log`. The formular for the sigmoid/logistic curve 
will be transformed as...

### $\frac{1}{(1+e^{-p_2 \times (log(\frac{x}{p_3}))})}$

```{r chunk1a}
sigmoid2 = function(x, p2, p3) {1 / (1 + exp(-p2 * (log(x/p3))))}
curve(sigmoid2(x, p2=20, p3=3), from=0.01, to=+10)
abline(v=3, lty=2)
```


***

### Transformed Positive Sigmoid

If we move `p2` inside the `log` followed by logarithm exponentiation we'll get

### $\frac{1}{1+(\frac{p_3}{x})^{p_2}}$

```{r chunk1b}
sigmoid3 = function(x, p2, p3) {1 / (1 + (p3/x)^p2)}
curve(sigmoid3(x, p2=20, p3=3), from=0.01, to=+10)
abline(v=3, lty=2)
# smoother
curve(sigmoid3(x, p2=4, p3=3), from=0.01, to=+10, add=T, col='navyblue')
```


In case we need to model an opposite dependency the trend has to be reversed.
For example we want to formalize a probablity of chemical compound being missed 
in analysis as a function of intensity.

### $\frac{1}{1+(\frac{x}{p_3})^{p_2}}$

```{r chunk1c}
sigmoid3 = function(x, p2, p3) {1 / (1 + (x/p3)^p2)}
curve(sigmoid3(x, p2=20, p3=3), from=0.01, to=+10)
abline(v=3, lty=2)
# smoother
curve(sigmoid3(x, p2=4, p3=3), from=0.01, to=+10, add=T, col='navyblue')
```



***

### Arctangent

Another way of modeling sigmoid dependency.

### $\frac{2}{\pi} \times arctan((x-p3) \times p2)$

The notation of parameters as above:

`p2` - shaprness

`p3` - position of 50% change

```{r chunk2}
sigmoid2 = function(x, sharpness, threshold) (2/pi)*atan((x-threshold)*sharpness)
curve(sigmoid2(x, sharpness=1, threshold=2), from=-10, to=+10)
curve(sigmoid2(x, sharpness=3, threshold=2), from=-10, to=+10, add=TRUE, col='blue')
abline(v=2)
```



